\sysfull

### 2018-04-15 paper/systemdescription.tex
enrich the system overview

\textbf{\sys Task Downscaling Manager.} \textcolor{red}{\sys's downscaling manager is responsible for preserving the forward progress when \sys repeatedly fails on a single static task. The downscaling manager utilizes a timer-based technique and relies on the virtual memory manager to gain a full \emph{flexibility} on where to split a task. These features distinguish \sys task splitting technique from the traditional checkpointing. A checkpointing system that uses voltage threshold to place a checkpoint might cause a program to crash if the checkpoint happened to be placed between a peripheral initialization and its call. If a programmer disables the interrupts around this section of the code, the program may fail indefinitely to progress since the checkpoint may only be deferred. On a repeated failure the \sys task downscaling manager places the \emph{partial commit} after a shorter time than the one before to guarantee forward progress. Details of task downscaling are presented in Section~\ref{sec:task_downsizing}.}

>>>>

\textbf{\sys Task Downscaling Manager.} \textcolor{red}{\sys's downscaling manager is responsible for preserving the forward progress when \sys repeatedly fails on a single static task. The downscaling manager utilizes a timer-based technique and relies on the virtual memory manager to gain a full \emph{flexibility} on where to split a task. These features distinguish \sys task splitting technique from the traditional checkpointing. A checkpointing system that uses voltage threshold to place a checkpoint might cause a program to crash if the checkpoint happened to be placed between a peripheral initialization and its call. If a programmer disables interrupts between the peripheral initialization and the call, the program may fail indefinitely to progress since the checkpoint may only be deferred. The \sys task downscaling manager, on the other hand,  triggers  a \emph{partial commit} faster than the previous one on a repeated failure to guarantee forward progress. Details of task downscaling are presented in Section~\ref{sec:task_downsizing}.}
